---
title: "Dec_25_2018_Venn_Diagrams"
author: "Yasmin Rajendran"
date: "December 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,Library, warning=FALSE,message=FALSE, echo=FALSE,results='hide'}
library(edgeR)
library(limma)
library(reshape2)
library(gsubfn)
library(plyr)
library(dplyr)
library(DataCombine)
library(RFLPtools)
library(gdata)
library(stats)
library(factoextra)
library("biomaRt")
library(knitr)
library(org.Dr.eg.db)
library(clusterProfiler)
library(gtools)
library(data.table)
library(tidyr)
library(gplots)
library(RColorBrewer)
library("biomaRt")
library(ggplot2)
library(gridExtra)
library(knitr)
library(ggmap)
library(VennDiagram)
```

**Step 1**: Join the counts matrix to the Ensembl IDs. Do the 1 Way ANOVA with an FDR restriction. Create pie charts as well.

```{r Counts_Matrix_To_Ensembl_IDs, echo=TRUE,warning=FALSE,message=FALSE, echo=FALSE,results='hide'}
remove(list = ls())

data <- read.delim("all.counts2_6_20_2018.txt", row.names=1, header=T)



colnames( data ) <- paste(c("W", "W", "W", 
                            "Ac", "Ac", "Ac", 
                            "Hg001", "Hg001", "Hg001",
                            "Hg01", "Hg01", "Hg01", 
                            "Hg1", "Hg1", "Hg1", 
                            "Tc01", "Tc01", "Tc01", 
                            "Tc1", "Tc1", "Tc1", 
                            "Tc01.Hg01", "Tc01.Hg01", "Tc01.Hg01", 
                            "Tc01.Hg1", "Tc01.Hg1", "Tc01.Hg1",
                            "Tc1.Hg01", "Tc1.Hg01","Tc1.Hg01", 
                            "Tc1.Hg1", "Tc1.Hg1", "Tc1.Hg1"),sep="")

group <- c("W", "W", "W", 
           "Ac", "Ac", "Ac", 
           "Hg001", "Hg001", "Hg001",
           "Hg01", "Hg01", "Hg01", 
           "Hg1", "Hg1", "Hg1", 
           "Tc01", "Tc01", "Tc01", 
           "Tc1", "Tc1", "Tc1", 
           "Tc01.Hg01", "Tc01.Hg01", "Tc01.Hg01", 
           "Tc01.Hg1", "Tc01.Hg1", "Tc01.Hg1",
           "Tc1.Hg01", "Tc1.Hg01","Tc1.Hg01", 
           "Tc1.Hg1", "Tc1.Hg1", "Tc1.Hg1")


# Do normalization after merging in UniRef100 IDs

# Import blast file

Blasted_2 <-  read.table("Tom_v_Zf_6_20_2018.blast", sep = "\t")
options(scipen = 999)

colnames(Blasted_2) <- c("XLOC", "UniRef100","Col3", "Col4", "Col5")

Blasted_2 <- Blasted_2[ -c(3:5) ]

Blasted_Again <-  as.data.frame(lapply(Blasted_2[1:2], sub, pattern="\\s+.*", replacement=""))

data <- cbind(XLOC = rownames(data), data) 

Merged_UniRef <- merge(Blasted_Again, as.matrix(data), by = "XLOC")

Removal <- c("XLOC")

Removal_1 <- Merged_UniRef[ , !(names(Merged_UniRef) %in% Removal)]

x_dt_aggreg <- aggregate(. ~ UniRef100, Removal_1, sum)

Merged_UniRef <- x_dt_aggreg[,-1]
rownames(Merged_UniRef) <- x_dt_aggreg[,1]

# Take (non-normalized data) data and isolate the first column

First_Col <-  as.data.frame( as.matrix(rownames(Merged_UniRef)) )

rownames(data) <- NULL

write.table(First_Col, file = "UniRef_100_IDs.txt", sep = " ", row.names= FALSE, col.names = FALSE )

#Go to https://www.uniprot.org/uploadlists/ and convert from UniRef100 IDs to UniProtK

#Copied to Notepad ++ and removed all the quotes. Then copied the list to the site.

colnames(First_Col) <- "UniRef100"

UniRef100_to_UniProtKB <- read.table( "Mapping_Table_UniRef_100_to_UniProtKB", sep="\t", header=TRUE, fill = TRUE)

colnames(UniRef100_to_UniProtKB) <- c("UniRef100", "UniProtKB" )

UniRef100_to_UniProtKB_merge_to_data <- merge(First_Col, UniRef100_to_UniProtKB, by = "UniRef100")

colnames(UniRef100_to_UniProtKB_merge_to_data)[2] <- "UniProtKB"

write.table(  (UniRef100_to_UniProtKB_merge_to_data[2] ), file = "UniProtKB.txt", sep = " ", row.names= FALSE, col.names = FALSE)

##Look up the IDs in David restricting to the Zebrafish IDs.

UniProtKB_Ensembl <- read.table("Dec_20_2018_UniProtKB_to_Ensembl_ID_From_David.txt", sep="\t")

head(UniProtKB_Ensembl)

UniProtKB_Ensembl_IDs_Only <- UniProtKB_Ensembl

# Remove the species name column and the gene name column leaving the UniProtKB ID column and the Ensembl ID column

UniProtKB_Ensembl_IDs_Only <- UniProtKB_Ensembl_IDs_Only [, -c(3:4)] 

#Remove the first row as it contains the words "From" and "To"

UniProtKB_Ensembl_IDs_Only <- UniProtKB_Ensembl_IDs_Only [-1,]

# Name the columns

names(UniProtKB_Ensembl_IDs_Only) <- c("UniProtKB", "Ensembl_ID")

Merge_All_UniProtKB_UniRef100_Ensembl <- merge(UniProtKB_Ensembl_IDs_Only, UniRef100_to_UniProtKB, by = "UniProtKB")

Dt_and_Merge_All <- merge (Merge_All_UniProtKB_UniRef100_Ensembl, x_dt_aggreg, by = "UniRef100" )

Ensembl_ID_data_set <- Dt_and_Merge_All[ , -which(names(Dt_and_Merge_All) %in% c("UniRef100","UniProtKB"))]

#Now on to aggregating by ID. 

rm(list=setdiff(ls(), "Ensembl_ID_data_set"))

Data_with_Ensembl_IDs_1 <- aggregate(. ~ Ensembl_ID, data = Ensembl_ID_data_set, sum)

Data_with_Ensembl_IDs_1_1 <- transform(Data_with_Ensembl_IDs_1, 
                          W = as.numeric(W), 
                          W.1 = as.numeric(W.1),
                          W.2 = as.numeric(W.2),
                   
                           Ac = as.numeric(Ac),
                         Ac.1 = as.numeric(Ac.1),
                         Ac.2 = as.numeric(Ac.2),
                   
                        Hg001 = as.numeric(Hg001),
                      Hg001.1 = as.numeric(Hg001.1),
                      Hg001.2 = as.numeric(Hg001.2),

                        Hg01 = as.numeric(Hg01),
                      Hg01.1 = as.numeric(Hg01.1),
                      Hg01.2 = as.numeric(Hg01.2),

                         Hg1 = as.numeric(Hg1),
                       Hg1.1 = as.numeric(Hg1.1),
                       Hg1.2 = as.numeric(Hg1.2),

                        Tc01 = as.numeric(Tc01),
                      Tc01.1 = as.numeric(Tc01.1),
                      Tc01.2 = as.numeric(Tc01.2),

                        Tc1 = as.numeric(Tc1),
                      Tc1.1 = as.numeric(Tc1.1),
                      Tc1.2 = as.numeric(Tc1.2),
                        
                  Tc01.Hg01 = as.numeric(Tc01.Hg01),
                Tc01.Hg01.1 = as.numeric(Tc01.Hg01.1),
                Tc01.Hg01.2 = as.numeric(Tc01.Hg01.2),

                   Tc01.Hg1 = as.numeric(Tc01.Hg1),
                 Tc01.Hg1.1 = as.numeric(Tc01.Hg1.1),
                 Tc01.Hg1.2 = as.numeric(Tc01.Hg1.2),

                   Tc1.Hg01 = as.numeric(Tc1.Hg01),
                 Tc1.Hg01.1 = as.numeric(Tc1.Hg01.1),
                 Tc1.Hg01.2 = as.numeric(Tc1.Hg01.2),

                    Tc1.Hg1 = as.numeric(Tc1.Hg1),
                  Tc1.Hg1.1 = as.numeric(Tc1.Hg1.1),
                  Tc1.Hg1.2 = as.numeric(Tc1.Hg1.2) )



M_N_1 <- as.matrix(Data_with_Ensembl_IDs_1_1)

M_N_2 <- M_N_1[,-1]
rownames(M_N_2) <- M_N_1[,1]
M_N_1_ME <- M_N_2

M_N_1_ME_1 <- transform(M_N_1_ME, 
                          W = as.numeric(W), 
                          W.1 = as.numeric(W.1),
                          W.2 = as.numeric(W.2),
                   
                           Ac = as.numeric(Ac),
                         Ac.1 = as.numeric(Ac.1),
                         Ac.2 = as.numeric(Ac.2),
                   
                        Hg001 = as.numeric(Hg001),
                      Hg001.1 = as.numeric(Hg001.1),
                      Hg001.2 = as.numeric(Hg001.2),

                        Hg01 = as.numeric(Hg01),
                      Hg01.1 = as.numeric(Hg01.1),
                      Hg01.2 = as.numeric(Hg01.2),

                         Hg1 = as.numeric(Hg1),
                       Hg1.1 = as.numeric(Hg1.1),
                       Hg1.2 = as.numeric(Hg1.2),

                        Tc01 = as.numeric(Tc01),
                      Tc01.1 = as.numeric(Tc01.1),
                      Tc01.2 = as.numeric(Tc01.2),

                        Tc1 = as.numeric(Tc1),
                      Tc1.1 = as.numeric(Tc1.1),
                      Tc1.2 = as.numeric(Tc1.2),
                        
                  Tc01.Hg01 = as.numeric(Tc01.Hg01),
                Tc01.Hg01.1 = as.numeric(Tc01.Hg01.1),
                Tc01.Hg01.2 = as.numeric(Tc01.Hg01.2),

                   Tc01.Hg1 = as.numeric(Tc01.Hg1),
                 Tc01.Hg1.1 = as.numeric(Tc01.Hg1.1),
                 Tc01.Hg1.2 = as.numeric(Tc01.Hg1.2),

                   Tc1.Hg01 = as.numeric(Tc1.Hg01),
                 Tc1.Hg01.1 = as.numeric(Tc1.Hg01.1),
                 Tc1.Hg01.2 = as.numeric(Tc1.Hg01.2),

                    Tc1.Hg1 = as.numeric(Tc1.Hg1),
                  Tc1.Hg1.1 = as.numeric(Tc1.Hg1.1),
                  Tc1.Hg1.2 = as.numeric(Tc1.Hg1.2) )


M_N_1_ME_1 <- data.frame(Ensembl = row.names(M_N_1_ME_1), M_N_1_ME_1)

rownames(M_N_1_ME_1) <- NULL

colnames( M_N_1_ME_1 ) <- paste(c("Ensembl",
                             "W", "W", "W", 
                            "Ac", "Ac", "Ac", 
                            "Hg001", "Hg001", "Hg001",
                            "Hg01", "Hg01", "Hg01", 
                            "Hg1", "Hg1", "Hg1", 
                            "Tc01", "Tc01", "Tc01", 
                            "Tc1", "Tc1", "Tc1", 
                            "Tc01.Hg01", "Tc01.Hg01", "Tc01.Hg01", 
                            "Tc01.Hg1", "Tc01.Hg1", "Tc01.Hg1",
                            "Tc1.Hg01", "Tc1.Hg01","Tc1.Hg01", 
                            "Tc1.Hg1", "Tc1.Hg1", "Tc1.Hg1"),sep="")
group <- c("W", "W", "W", 
           "Ac", "Ac", "Ac", 
           "Hg001", "Hg001", "Hg001",
           "Hg01", "Hg01", "Hg01", 
           "Hg1", "Hg1", "Hg1", 
           "Tc01", "Tc01", "Tc01", 
           "Tc1", "Tc1", "Tc1", 
           "Tc01.Hg01", "Tc01.Hg01", "Tc01.Hg01", 
           "Tc01.Hg1", "Tc01.Hg1", "Tc01.Hg1",
           "Tc1.Hg01", "Tc1.Hg01","Tc1.Hg01", 
           "Tc1.Hg1", "Tc1.Hg1", "Tc1.Hg1")

M_N_1_ME_1 <- as.data.frame(as.matrix(M_N_1_ME_1) )

M_N_1_ME_1_1 <- M_N_1_ME_1[,-1]
rownames(M_N_1_ME_1_1) <- M_N_1_ME_1[,1]

M_N_1_ME_1_1[which( sapply( M_N_1_ME_1_1, class ) == 'factor' )] <- lapply( M_N_1_ME_1_1[which( sapply( M_N_1_ME_1_1, class ) == 'factor' )], function(x) as.numeric(as.character(x)) )

# Counts with Ensembl IDs

a <- as.matrix(M_N_1_ME_1_1)

Counts_Data_Set_With_Aggregated_Ensembl_IDs <- a

rm(list=setdiff(ls(), c("Counts_Data_Set_With_Aggregated_Ensembl_IDs", "group")) )


# A dge list of the counts

M_N <- DGEList(counts=  ( Counts_Data_Set_With_Aggregated_Ensembl_IDs ), group = group)

# Now on to making DGElist

keep <- rowSums(cpm(M_N)>1) >= 5

kdge <- M_N [keep,]

# Make a design matrix

data_for_design_matrix <- read.csv("Experiment_Design.csv", header = TRUE, sep = ",")

# Making a model.matrix Refered to: page 65 of EdgeR Manual

design_1 <- model.matrix(~ Stressor, data= data_for_design_matrix)
  
# The low counts are filtered in kdge

y <- kdge

y <- estimateDisp(y ,design_1, robust=TRUE)

fit <- glmQLFit(y, design_1, robust=TRUE)

List_of_colnames_design  <- (  c( colnames(fit) ) )

n_max <-nrow(Counts_Data_Set_With_Aggregated_Ensembl_IDs)

for (i in (1:ncol(fit)) ) {
  
  qlf  <- glmQLFTest(fit, coef=i)
  
  Storing_qlf <- topTags(qlf, n = n_max)
  
  # Store as a data frame
  
  Df_qlf_stored <-  as.data.frame(Storing_qlf)
  
  # Restrict b P Value less than or equal to 0.01
  
  P_Val_Point01 <- subset(Df_qlf_stored, PValue <= 0.01)
  
  # Restrict b FDR less than or equal to 0.05
  
  FDR_0.05_Restriction <- subset(P_Val_Point01, FDR <= 0.05)
  
  # Store the IDs in a file for each treatment (with P value and FDr restrictions)
  
  file_name <- (c((paste(List_of_colnames_design[i],"P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv",sep = "_"))))
  
  write.csv( FDR_0.05_Restriction, file = file_name)
  
  q <- list(FDR_0.05_Restriction)
  
  counter = 0
  
  for (p_val_FDR in q) {
    
    counter = counter + 1
    Up_reg<- sum(p_val_FDR[,"logFC"] > 0)
    Down_reg  <- sum(p_val_FDR[,"logFC"] < 0)
    
    Tabl_Up_and_Down_Vals <- as.matrix(c(Up_reg,Down_reg),ncol=1,byrow=TRUE) 
    colnames(Tabl_Up_and_Down_Vals) <- c("a")
    rownames(Tabl_Up_and_Down_Vals) <- c("Up","Down") 
    Tabl_Up_and_Down_Vals_1 <- Tabl_Up_and_Down_Vals
    Table_DT <- setDT(as.data.frame(Tabl_Up_and_Down_Vals), 
                      keep.rownames = TRUE)[]
    Tabl_Up_Down_PVal <- as.data.frame(Table_DT)
    names(Tabl_Up_Down_PVal)[names(Tabl_Up_Down_PVal) == "rn"] <- "Regulation"
    rownames(Tabl_Up_Down_PVal) <- NULL
    
    List_names <- list("P_Val_Point01_Plus_FDR05")
    
    # Since FDR is restricted to less than or equal to 0.1 for the ones with FDR restriction I am just placing FDR next to the ones with an FDR Restriction
    
    List_names_1_for_title_ggplot <- list("")
    
    List_of_colnames_design_1 <- c("(Intercept)", "Hg001", "Hg01", "Hg1",
                                   "TCDD01", 
                                   "in the Low Dose Combination",
                                   "TCDD01.Hg1",
                                   "TCDD1", "TCDD1.Hg01", 
                                   "in the High Dose Combination",
                                   "Water")
    
    pie_chart_ggplot <- ggplot(Tabl_Up_Down_PVal, aes(x= "", y= a, fill= Regulation)) + geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0) + 
      geom_text(aes( label = paste(rownames(Tabl_Up_and_Down_Vals_1) , (round (  (( c(Up_reg, Down_reg) )/sum(( c(Up_reg, Down_reg) ))*100) )  ), "%", sep = " ")), position = position_stack(vjust = 0.5) ) +
      ggtitle(c((paste("Percentage Of RNAs Affected ", List_of_colnames_design_1[i], List_names_1_for_title_ggplot[counter] , sep = " ", collapse = NULL)))) + theme(axis.text = element_blank(),axis.ticks = element_blank(), panel.grid  = element_blank(), legend.title=element_blank(), axis.title = element_blank(), panel.background = element_blank())
    
    colnames(Tabl_Up_Down_PVal)[2] <- "The Number Of RNAs"
    
    jpeg(c((paste("GGPlotPie_Chart_Thesis_Paper", List_of_colnames_design_1[i], List_names[counter],".jpg" ,sep = " ", collapse = NULL))))
    grid.arrange(pie_chart_ggplot, tableGrob(Tabl_Up_Down_PVal),ncol=1 )
    dev.off()
    
    grid.arrange(pie_chart_ggplot, tableGrob(  Tabl_Up_Down_PVal),ncol=1 )
    
  }
  
  
}
```

**Pre-Step 2:** Load the files with the restricted p value and FDR.

```{r}

# TCDD treatments

Tc1_Post_Test_Restricted <- read.csv("StressorTCDD1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

Tc01_Post_Test_Restricted <- read.csv("StressorTCDD01_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

# Hg treatments

Hg1_Post_Test_Restricted <- read.csv("StressorHg1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

Hg01_Post_Test_Restricted <- read.csv("StressorHg01_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

Hg001_Post_Test_Restricted <-
  read.csv("StressorHg001_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

# Combination treatments

LD_Combin_Test_Restricted <- read.csv("StressorTCDD01_Hg01_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

HD_Combin_Test_Restricted <- read.csv("StressorTCDD1_Hg1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")
```





**Step 2:** Start making venn diagrams.


**Step 2a:** Make a venn diagram of Tc01 vs Tc1. 
```{r Tc01_vs_Tc1}

n1   <-  (na.omit((Tc01_Post_Test_Restricted[,1])   ))
n2   <-  (na.omit((Tc1_Post_Test_Restricted[,1])   ))


Tc01_vs_Tc1_Venn_Diagram <- draw.pairwise.venn(
area1 = as.numeric(length (n1)),
area2 = as.numeric(length (n2)),
cross.area = as.numeric(length (intersect(n1,n2) ) ),
category = c("Low Dose", "High Dose"),
fill = c("blue", "red"),
cex = 2,
cat.cex = rep(2, 2),
cat.fontface = rep("plain", 2),
cat.just = list(c(0.9, -8), c(0.2, -13) ),
scaled = TRUE,
 cat.default.pos = "outer", cat.prompts = FALSE, rotation.degree = 0, rotation.centre = c(0.5, 0.5), direct.area = FALSE, area.vector = 0
);
grid.draw(Tc01_vs_Tc1_Venn_Diagram);
grid.newpage();
```

**Step 2b:** Make a venn diagram comparing the mercury doses. 

```{r Mercury_Dose_Comparisons}

#All Hgs compared

n1   <-  (na.omit(  (Hg1_Post_Test_Restricted[,1])   ))
n2   <-  (na.omit(  (Hg01_Post_Test_Restricted[,1])  ))
n3   <-  (na.omit(  (Hg001_Post_Test_Restricted[,1])  ))
n12  <-        intersect( n1, n2) 
n13  <-        intersect( n1, n3)
n23  <-        intersect( n2, n3)
n123 <-        intersect( n1, (intersect(n2, n3)) )


Hgs_Compared <- draw.triple.venn(
  
                                      area1 = length(n1  ) , 
                                      area2 = length(n2  ) , 
                                      area3 = length(n3  ) ,
                                      n12   = length(n12 ) , 
                                      n23   = length(n23 ) , 
                                      n13   = length(n13 ) , 
                                      n123  = length(n123) ,
                                      category = c("Hg1", "Hg01", "Hg001"),
                                      fill    = c("darkseagreen1", "lightsalmon", "lightsalmon3"),
                                      cat.cex = rep(2, 3), cat.fontface = rep("plain", 3),
                                      cat.fontfamily = rep("serif", 3), 
                                      cat.just =list(c(0.5, 1), c(0.5, 1), c(0.5, 0)), 
                                      cat.default.pos = "outer", 
                                      cat.prompts = FALSE, 
                                      rotation.centre = c(0.5, 0.5), 
                                      print.mode = "raw",
                                      sigdigs = 3,
                                      euler.d = TRUE);
grid.draw(Hgs_Compared);
grid.newpage();


```

**Step 2c:** Make a venn diagram comparing Tc01 and the mercury doses.

```{r Tc01_vs_mercury_doses}
# Tc01 vs All Hg Alone

n1   <-  (na.omit((Tc01_Post_Test_Restricted[,1])   ))
n2   <-  (na.omit((Hg1_Post_Test_Restricted[,1])   ))
n3   <-  (na.omit((Hg01_Post_Test_Restricted[,1])  ))
n4   <-  (na.omit((Hg001_Post_Test_Restricted[,1])  ))

n12  <-        intersect( n1, n2)

n13  <-        intersect( n1, n3)

n14  <-        intersect( n1, n4)   

n23  <-        intersect( n2, n3)   

n24  <-        intersect( n2, n4)  

n34  <-        intersect( n3, n4)  

n123 <-        intersect( n1, (intersect(n2, n3)) )   

n124 <-        intersect( n1, (intersect(n2, n4)) ) 

n134 <-        intersect( n1, (intersect(n3, n4)) )  

n234 <-        intersect( n2, (intersect(n3, n4)) )  

n1234 <-       intersect( n1,intersect( n2, (intersect(n3, n4)) ) )

Tc01_vs_All_Hg_Alone <- draw.quad.venn(
  area1 = as.numeric(length( n1    )), 
  area2 = as.numeric(length( n2    )),  
  area3 = as.numeric(length( n3    )),
  area4 = as.numeric(length( n4    )), 
  n12   = as.numeric(length( n12   )),
  n13   = as.numeric(length( n13   )), 
  n14   = as.numeric(length( n14   )), 
  n23   = as.numeric(length( n23   )), 
  n24   = as.numeric(length( n24   )),
  n34   = as.numeric(length( n34   )), 
  n123  = as.numeric(length( n123  )), 
  n124  = as.numeric(length( n124  )),
  n134  = as.numeric(length( n134  )), 
  n234  = as.numeric(length( n234  )), 
  n1234 = as.numeric(length( n1234 )), 
  category = c("TCDD LD", "Hg HD", "Hg MD", "Hg LD"),
  fill = c("red", "cyan", "cornflowerblue", "blue"),
  cat.col = c("red", "cyan", "cornflowerblue", "blue"),
  cat.cex = rep(1, 4), 
  cat.fontface = rep("plain", 4),
  cat.fontfamily = rep("serif", 4), 
  cat.just = rep(list(c(0.5, 0.5)), 4), 
  rotation.degree = 0,
  rotation.centre = c(0.5, 0.5), 
  ind = TRUE, 
  cex.prop = NULL, 
  print.mode = "raw", sigdigs = 3, 
  direct.area = FALSE, 
  area.vector = 0,
  euler.d = TRUE
    );
grid.draw(Tc01_vs_All_Hg_Alone);
grid.newpage();
```

**Step 2d:** Make a venn diagram comparing Tc1 and the mercury doses.

```{r Tc1_vs_Hg_doses}
# Tc1 vs All Hg Alone

n1   <-  (na.omit((Tc1_Post_Test_Restricted[,1])   ))
n2   <-  (na.omit((Hg1_Post_Test_Restricted[,1])   ))
n3   <-  (na.omit((Hg01_Post_Test_Restricted[,1])  ))
n4   <-  (na.omit((Hg001_Post_Test_Restricted[,1])  ))

n12  <-        intersect( n1, n2)

n13  <-        intersect( n1, n3)

n14  <-        intersect( n1, n4)   

n23  <-        intersect( n2, n3)   

n24  <-        intersect( n2, n4)  

n34  <-        intersect( n3, n4)  

n123 <-        intersect( n1, (intersect(n2, n3)) )   

n124 <-        intersect( n1, (intersect(n2, n4)) ) 

n134 <-        intersect( n1, (intersect(n3, n4)) )  

n234 <-        intersect( n2, (intersect(n3, n4)) )  

n1234 <-       intersect( n1,intersect( n2, (intersect(n3, n4)) ) )

Tc01_vs_All_Hg_Alone <- draw.quad.venn(
  area1 = as.numeric(length( n1    )), 
  area2 = as.numeric(length( n2    )),  
  area3 = as.numeric(length( n3    )),
  area4 = as.numeric(length( n4    )), 
  n12   = as.numeric(length( n12   )),
  n13   = as.numeric(length( n13   )), 
  n14   = as.numeric(length( n14   )), 
  n23   = as.numeric(length( n23   )), 
  n24   = as.numeric(length( n24   )),
  n34   = as.numeric(length( n34   )), 
  n123  = as.numeric(length( n123  )), 
  n124  = as.numeric(length( n124  )),
  n134  = as.numeric(length( n134  )), 
  n234  = as.numeric(length( n234  )), 
  n1234 = as.numeric(length( n1234 )), 
  category = c("TCDD HD", "Hg HD", "Hg MD", "Hg LD"),
  fill = c("red", "cyan", "cornflowerblue", "blue"),
  cat.col = c("red", "cyan", "cornflowerblue", "blue"),
  cat.cex = rep(1, 4), 
  cat.fontface = rep("plain", 4),
  cat.fontfamily = rep("serif", 4), 
  cat.just = rep(list(c(0.5, 0.5)), 4), 
  rotation.degree = 0,
  rotation.centre = c(0.5, 0.5), 
  ind = TRUE, 
  cex.prop = NULL, 
  print.mode = "raw", sigdigs = 3, 
  direct.area = FALSE, 
  area.vector = 0,
  euler.d = TRUE
    );
grid.draw(Tc01_vs_All_Hg_Alone);
grid.newpage();

```

**Step 2e:** Make a venn diagram comparing the low dose treatments.

```{r LowDosesOfHgAloneTCDD_Alone_And_In_Combination}

n1   <-  (na.omit((Hg01_Post_Test_Restricted[,1]     )   ))
n2   <-  (na.omit((Tc01_Post_Test_Restricted[,1]     )   ))
n3   <-  (na.omit((LD_Combin_Test_Restricted[,1]     )   ))
n12  <-        intersect( n1, n2)
n13  <-        intersect( n1, n3)
n23  <-        intersect( n2, n3)
n123 <-        intersect( n1, (intersect(n2, n3)) )

LowDosesOfHgAloneTCDD_Alone_And_In_Combination <- draw.triple.venn(
  
                                      area1 = length(n1  ) , 
                                      area2 = length(n2  ) , 
                                      area3 = length(n3  ) ,
                                      n12   = length(n12 ) , 
                                      n23   = length(n23 ) , 
                                      n13   = length(n13 ) , 
                                      n123  = length(n123) ,
                                      category = c("Mercury Low Dose", "TCDD Low Dose", "TCDD & Hg Both Low Dose"),
                                      fill    = c("green", "lightsalmon", "blue"),
                                      cat.col = c("black", "black", "black"),
                                      cat.cex = rep(1, 3), cat.fontface = rep("plain", 3),
                                      cat.fontfamily = rep("serif", 3), cat.just =list(c(0.5, 1), c(0.5, 1), c(0.5, 0)), cat.default.pos = "text", cat.prompts = FALSE, rotation.degree = 0, rotation.centre = c(0.5, 0.5), ind = TRUE, sep.dist = 0.05, offset = 0, cex.prop = NULL, print.mode = "raw",sigdigs = 3, direct.area = FALSE, area.vector = 0);
grid.draw(LowDosesOfHgAloneTCDD_Alone_And_In_Combination);
grid.newpage()
```

**Step 2f:** Make a venn diagram comparing the high dose treatments.

```{r HigDoseAll_Compared_To_Ensembl}

n1   <-  (na.omit((Hg1_Post_Test_Restricted[,1]     )   ))
n2   <-  (na.omit((Tc1_Post_Test_Restricted[,1]     )   ))
n3   <-  (na.omit((HD_Combin_Test_Restricted[,1]    )   ))
n12  <-        intersect( n1, n2)
n13  <-        intersect( n1, n3)
n23  <-        intersect( n2, n3)
n123 <-        intersect( n1, n23 )


HighDosesOfHgAloneTCDD_Alone_And_In_Combination <- draw.triple.venn(
  
                                      area1 = length(n1  ) , 
                                      area2 = length(n2  ) , 
                                      area3 = length(n3  ) ,
                                      n12   = length(n12 ) , 
                                      n23   = length(n23 ) , 
                                      n13   = length(n13 ) , 
                                      n123  = length(n123) ,
                                      category = c("Mercury High Dose", "TCDD High Dose", "TCDD & Hg Both High Dose"),
                                      fill    = c("green", "lightsalmon", "blue"),
                                      cat.col = c("black", "black", "black"),
                                      cat.cex = rep(1, 3), cat.fontface = rep("plain", 3),
                                      cat.fontfamily = rep("serif", 3), cat.just =list(c(0.5, 1), c(0.5, 1), c(0.5, 0)), cat.default.pos = "text", cat.prompts = FALSE, rotation.degree = 0, rotation.centre = c(0.5, 0.5), ind = TRUE, sep.dist = 0.05, offset = 0, cex.prop = NULL, print.mode = "raw",sigdigs = 3, direct.area = FALSE, area.vector = 0, scaled = TRUE, euler.d = TRUE);
grid.draw(HighDosesOfHgAloneTCDD_Alone_And_In_Combination);
grid.newpage()
```

**Step 3:** Move on to making comparisons of the ANOVA results. 

```{r}
remove(list = ls())

TCDD_P_Val_Point01_Plus_FDR05 <- read.csv("StressorTCDD1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

Hg_P_Val_Point01_Plus_FDR05 <- read.csv("StressorHg1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")

Combination_P_Val_Point01_Plus_FDR05 <- read.csv("StressorTCDD1_Hg1_P_Val_FDR_Restricted_One_Way_ANOVA_Final.csv", header = TRUE, sep = ",")
```


**Step 8**: How many genes are in the combination treatment.

```{r}
nrow(Combination_P_Val_Point01_Plus_FDR05)
```

**Step 9**: How many genes are in the TCDD treatment.

```{r}
nrow(TCDD_P_Val_Point01_Plus_FDR05)
```


**Step 10**: How many genes are in the Hg treatment.

```{r}
nrow(Hg_P_Val_Point01_Plus_FDR05)
```


**Step 11a**: How many genes are common between Combination and TCDD.

```{r}
(length (intersect (Combination_P_Val_Point01_Plus_FDR05[,1], 
          TCDD_P_Val_Point01_Plus_FDR05[,1]) ) )
```

**Step 11b**: What percent of genes in the combination treatment are in common with TCDD?

```{r}

# (Total genes in common / genes only in Combination treatment ) *100

((length (intersect (Combination_P_Val_Point01_Plus_FDR05[,1], 
          TCDD_P_Val_Point01_Plus_FDR05[,1]) ) ) / nrow(Combination_P_Val_Point01_Plus_FDR05) ) * 100


```

**Step 12a**: How many genes are common between Combination and Hg.

```{r}
(length (intersect (Combination_P_Val_Point01_Plus_FDR05[,1], 
          Hg_P_Val_Point01_Plus_FDR05[,1]) ) )
```

**Step 12b**: What percent of genes in the combination treatment are in common with Hg?

```{r}

# (Total genes in common / genes only in Combination treatment ) *100

(
 
  
   (
    
    length 
  
  (intersect (Combination_P_Val_Point01_Plus_FDR05[,1],
                     Hg_P_Val_Point01_Plus_FDR05[,1]) ) 
  
  )
  
 / nrow(Combination_P_Val_Point01_Plus_FDR05) 

  
 ) * 100


```

**Step 13a**: How many genes are common between TCDD and Hg.

```{r}
(length (intersect (TCDD_P_Val_Point01_Plus_FDR05[,1], 
          Hg_P_Val_Point01_Plus_FDR05[,1]) ) )
```

**Step 13b**: What percent of genes in the TCDD treatment are in common with Hg?

```{r}

# (Total genes in common / genes only in Combination treatment ) *100

(
 
  
   (
    
    length 
  
  (intersect (TCDD_P_Val_Point01_Plus_FDR05[,1],
                     Hg_P_Val_Point01_Plus_FDR05[,1]) ) 
  
  )
  
 / nrow(TCDD_P_Val_Point01_Plus_FDR05) 

  
 ) * 100


```

**Step 13c**: What percent of genes in the Combination treatment are unique to this treatment?


```{r}
Intersect_between_Combiantion_and_Hg <- (length (intersect (Combination_P_Val_Point01_Plus_FDR05[,1], 
          Hg_P_Val_Point01_Plus_FDR05[,1]) ) )

Intersect_between_Combiantion_and_TCDD <-(length (intersect (Combination_P_Val_Point01_Plus_FDR05[,1], 
          TCDD_P_Val_Point01_Plus_FDR05[,1]) ) )

Intersects_Alone <- Intersect_between_Combiantion_and_TCDD  + Intersect_between_Combiantion_and_Hg

# 100 - Percentage of Intersects of alone treatments with combination
 100 - ( (Intersects_Alone / nrow(Combination_P_Val_Point01_Plus_FDR05) )*100)
```

**Step 13d**: What genes are only effected by the intersects?

```{r}

Intersects_Alone
```


**Step 13e**: What genes are only effected by the combination treatment?

```{r}

length(Combination_P_Val_Point01_Plus_FDR05[,1]) - Intersects_Alone

```

